Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-15 article/article.tex

>>>>

The design of the robots and beacon can be split into 3 rough categories: first, the construction of the robot itself, including the design of the chassis; second, the integration of the bluetooth modules that were used to transmit and receive signals, and lastly, the algorithm and sensors used by the robot to orient itself and move towards the source of the signal.

\subsubsection{Robot Construction}
